National Longitudinal Evidence for Growth in Subjective Wellbeing from Spiritual Beliefs

### 2020-11-17 Analysis.Rmd
revisions to manuscript, worked out practical effect sizes

# Inference holds 
mod.1 <-lmer (PWI ~  1 +  Years * Beliefs +  Age.10yrs.C + Deprivation.S + Edu.S  + Employed + EthnicCats + Male  + Partner  + Pol.Orient.S + Urban + (1|Id), data= dfben, na.action = na.omit)
mod.2 <-lmer (LIFESAT ~ 1 + Years * Beliefs+ Age.10yrs.C + Deprivation.S + Edu.S  + Employed + EthnicCats + Male  + Partner  + Pol.Orient.S + Urban + (1|Id), data= dfben, na.action = na.omit)
summary(mod.1)
summary(mod.2)

@@

```{r cache = TRUE, dependson = "mod.1"}
#### Predicted Effects ####
pr.PWI <- ggpredict(model = mod.1, terms = c("Years [7:9]","Beliefs"), 
                    ci.lvl = 0.95,
                    type = "fe",
                    typical = "mean",
                   # condition = c(Euro =1),
                    back.transform = TRUE,
                    ppd = FALSE,
                    interval = "confidence")
p1<-plot(pr.PWI, facets = T) + 
 # scale_y_continuous(limits=c(4.75,5.25) )  + 
  gghighlight()  +  theme_blank()+ 
  ggtitle("Predicted Values of Personal Wellbeing") 
```
```{r pwi_expected}
```

```{r predictlifesat}
pr.LIFESAT <- ggpredict(model = mod.2, terms = c("Years [0:9]", "Beliefs"),
                        ci.lvl = 0.95,
                        type = "fe",
                        typical = "mean",
                     #   condition = c(Euro =1),
                        back.transform = TRUE,
                        ppd = FALSE,
                        interval = "confidence")
p2<-plot(pr.LIFESAT,facets = T) + 
 # scale_y_continuous(limits=c(6.35,6.85) ) + 
  gghighlight() + theme_blank() + 
  ggtitle("Predicted Values of Life Satisfaction") #+   scale_colour_brewer(palette = "Zissou1")
p2
```

>>>>

# Inference holds 
library(lme4)
mod.1 <-lmer (PWI ~  1 +  Years * Beliefs +  Age.10yrs.C + Deprivation.S + Edu.S  + Employed + EthnicCats + Male  + Partner  + Pol.Orient.S + Urban + (1|Id), data= dfben, na.action = na.omit)
mod.2 <-lmer (LIFESAT ~ 1 + Years * Beliefs+ Age.10yrs.C + Deprivation.S + Edu.S  + Employed + EthnicCats + Male  + Partner  + Pol.Orient.S + Urban + (1|Id), data= dfben, na.action = na.omit)
summary(mod.1)
summary(mod.2)

@@

```{r cache = TRUE, dependson = "mod.1"}
#### Predicted Effects ####
pr.PWI <- ggpredict(model = mod.1, terms = c("Years [0:9]","Beliefs"), 
                    ci.lvl = 0.95,
                    type = "fe",
                    typical = "mean",
                   # condition = c(Euro =1),
                    back.transform = TRUE,
                    ppd = FALSE,
                    interval = "confidence")
p1<-plot(pr.PWI, facets = T) + 
 # scale_y_continuous(limits=c(4.75,5.25) )  + 
  gghighlight()  +  theme_blank()+ 
  ggtitle("Predicted Values of Personal Wellbeing")

pr.PWI
```
```{r pwi_expected}
```

```{r predictlifesat}
pr.LIFESAT <- ggpredict(model = mod.2, terms = c("Years [0:9]", "Beliefs"),
                        ci.lvl = 0.95,
                        type = "fe",
                        typical = "mean",
                     #   condition = c(Euro =1),
                        back.transform = TRUE,
                        ppd = FALSE,
                        interval = "confidence")
# print expected intervals for the y-hats reported in the conclusion
pr.LIFESAT

p2<-plot(pr.LIFESAT,facets = T) + 
 # scale_y_continuous(limits=c(6.35,6.85) ) + 
  gghighlight() + theme_blank() + 
  ggtitle("Predicted Values of Life Satisfaction") #+   scale_colour_brewer(palette = "Zissou1")
p2
```
